---
title: "Lab 00 - Hello IDS!"
author: "Aniruddh Iyer"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Aniruddh Iyer", "Jacob Cullen", "Lucas Smith", 
           "Ethan Wood", "Athos Rocha", "Louis Newton"),
  github_username = c("aniruddhviyer", "s2543500", "ls657", 
                      "EJamesW05", "athos-roch", "LouisWeil"), 
  colour = c("navyblue", "blue", "hotpink", 
             "navyblue", "green", "turquoise"),
  hobby = c("Hiking", "Football", "Going Out", 
            "Reading Novels", "Karting", "Triathlon"),
  favourite_number = c(4, 8, 10, 10, 5, 7)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


This is a bar graph of a team member's github_username (x-axis) against their favourite_number (y-axis) in he favourite colour of each team member.

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "github_username", 
          y = "favourite_number",
          title = "Insert text here")
```

This is a bar graph of a team member's github_username (x-axis) against their favourite_number (y-axis) in he favourite colour of each team member.

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

A better representation of the data would be in the form of a pie chart.